Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-10 longoutput.tex
Fix bug on clock Hamiltonian
Add TODO

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates. TODO check if this is obvious. If not, explain why.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$

@@

>>>>

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
$$H_{clock}=\frac{1}{4}(Z_1 - Z_T) + \frac{1}{4}\sum_{t=1}^{T-1}(I-Z_tZ_{t+1}) $$
This can be checked by fixing the first and last qubit, then doing induction on the number of switches.

@@

TODO consider using the older construction with the angle between subspaces for better constants?
